---
title: "Preregistration: Bayesian Analysis for the Gender, Status, and Emotions Project"
author: "Suzanne Hoogeveen & Julia Haaf"
date: "10/15/2020"
bibliography: "MyBibs.bib"
csl: "apa6.csl"
header-includes:
  - \usepackage{marginnote}
  - \newcommand{\readme}[1]{\emph{\marginnote{Julia} (#1)}}
  - \newcommand{\readmoi}[1]{\emph{\marginnote{Suus} (#1)}}
output:
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library('diagram')
source("order-diagram.R")
```

# Overview

We outline a Bayesian analysis for the gender-and-anger backlash effect of Study 1 in the Gender, Status, and Emotion project: We will construct various hierarchical models that reflect the predictions from the proposed theories. The evidence for each of these different theories will be quantified by Bayes factor model comparison, following the approach by @haaf2017developing and @rouder2019beyond. In addition, we will adopt a multiverse approach in which we assess evidence for various a priori specified alternative analysis paths related to exclusion criteria [@steegen2016]. 

## The effect

This work involves a high-powered replication of the gender-and-anger backlash effect [@brescoll2008can]: whereas angry men in a professional context are accorded higher status, angry women are accorded lower status, compared to sad men and sad women, respectively. 
In addition to attempting to replicate this key effect, various theory-based alternative perspectives are compared. To this end, several moderator variables are added to the design. 

### Dependent variable

1. status conferral (1-11 scale)

### Main Independent Variables

1. target gender (male vs. female)
2. emotion (anger vs. sadness)
3. culture (West vs. East)

## Theoretical Perspectives

1. The *Gender Stereotyping* perspective predicts female managers suffer backlash and decrements in status for expressing anger because they have violated implicit prescriptive norms [@brescoll2008can]. 
2. The *Status Signaling* perspective predicts that anger projects dominance and status for both men and women. 
3. The *Cultural Change* perspective predicts that anger expressions lead to favorable evaluations of women relative to men, due to exposure to feminist messages and the #MeToo movement. (Effects are driven by internal motivations related to gender inequality.)
4. The *Study Savviness* perspective similarly predicts that angry women are favorably evaluated, but due to awareness of the study topic, external motivation not to appear prejudiced, and previous research experience. This should specifically apply to male participants, as they may be concerned about appearing sexist. (Effects are driven by external motivations related to self-presentation of not being sexist.)
5. The *Cultural Differences* perspective predicts that anger may have positive effects in Western cultures but negative effects in harmony-oriented Eastern cultures. 

These theoretical perspectives lead to the following predictions: 

1. Anger increases status conferral to male targets across all cultures, and decreases status conferral to female targets across all cultures.
2. Anger increases status conferral to all targets across all cultures.
3. Anger increases status conferral to female targets only, across all cultures, and female targets are generally accorded more status.
4. Anger increases status conferral to female targets only, across all cultures, and female targets are generally accorded more status. 
5. Anger increases status conferral to all targets, for all raters in Western societies, and decreases status conferral to all targets, for all raters in Eastern societies. 


```{r theoretical-ordering, warning=F, fig.height=7, fig.width=7, fig.cap="Theoretical positions are captured with order-constraints on cell means. Cells labeled 'a-m' correspond to the condition with an angry expression and a male target, cells labeled 's-m' correspond to the condition with a sad expression and a male target, cells labeled 'a-f' correspond to the condition with an angry expression and a female target, cells labeled 's-f' correspond to the condition with a sad expression and a female target.  \\textbf{A.} Gender Stereotyping model. \\textbf{B.} Status Signalling model. \\textbf{C.} Cultural Change / Study Savviness model. \\textbf{D.} Cultural Differences model for Westerners (D1) and for Easterners (D2). \\textbf{E.} Null model. \\textbf{F.} None-of-the-above alternative model where all orderings of cell means are possible."}
fig.ex1()
```

## Follow-up Analyses

In addition to the main tests of the theoretical perspectives, we will look at the following factors in follow-up tests:

- main effect of target gender: are male or female targets generally accorded more status? 
- gender of the rater: do male and female raters differentially display the main effects or interactions derived from the theoretical perspectives (e.g., do male or female raters particulartly show gender stereotyping effects or reversed gender biases?)
- individual differences: what are the effects of workplace gender beliefs, sexist beliefs, #MeToo exposure, internal motivation to respond without sexism, external motivation to respond without sexism, study experience (number of research studies participated in, participanted in similar study (yes/no), psychology course taken(yes/no)), suspicion (hypothesis about gender (yes/no), influenced by gender, influenced by emotion). 

These individual difference moderations will be used to distinguish between perspective 3 and 4, which predict the same overall pattern of responses, yet driven by different differences (see below). In addition, the moderator analyses will serve to further unpack what individual differences are related to the observed effects. 

### Moderators for individual differences  

1. No moderators 
2. No moderators 
3. Internal motivations related to gender inequality. This construct is relevant to theory 3. The main idea is that raters who are aware of and hold strong beliefs about the presence of gender inequality apply reversed gender stereotyping (favorably evaluating women). 
    a. Beliefs about gender inequality in the workplace (5 items) predict more status conferral to female targets
    b. Sexist beliefs (3 items) predict less status conferral to female targets
    c. Exposure to #MeToo movement (6 items) predicts more status conferral to female targets
    d. Internal motivation to respond without sexism (3 items) predicts more status conferral to female targets. 
4. External motivation related to self-presentation. This construct is relevant to theory 4. The main idea is that raters who are concerned about coming off as sexist apply reversed gender stereotyping (favorably evaluating women). 
    a. External motivation to respond without sexism (3 items) predicts more status conferral to female targets
    b. Number of research studies participated in predict more status conferral to female targets
    c. Participation in similar study (yes/no) predicts more status conferral to female targets
    d. Psychology course taken (yes/no) predicts more status conferral to female targets
    e. Suspicion about hypothesis being about gender (yes/no) predicts more conferral to female targets
    f. Awareness of being influenced by target gender (1-9 scale) predicts more conferral to female targets
    g. Awareness of being influenced by target emotion (1-9 scale) predicts more conferral to female targets
5. No moderators

# Multiverse Analysis

The multiverse approach allows us to assess the evidence across multiple potential sets of sample compositions, without a priori committing to any particular set of exclusion criteria or variable specifications [@steegen2016]. Nevertheless, for the primary analysis, we propose to include everyone who completed the relevant measures. Although for individual variables there are often exclusion criteria that might be preferred by researchers in the field for theoretical reasons (e.g., excluding subjects with less English experience or who fail to correctly recall the target gender), in practice, when many simultaneous exclusions are made the sample size can drop dramatically. In this case, effect size estimates may be inaccurate, it may not be possible to make any inference because of low sensitivity, and concerns are raised about differential attrition across conditions potentially confounding the results. Thus there is a principled case to be made on behalf of an intent-to-treat approach, in which few to no observations or participants are excluded [@gupta2011intentiontotreat; @mccoy2017understanding]. We consider the intent-to-treat principle a conservative but valuable approach that can be one key part of a multiverse analysis.

## Variables to include in the multiverse

###  Modeling-related dimensions

- Modeling random effects vs. common effects.
1. Use a common effect model
2. Use a varying effects model (random effects across regions)

While the random effects models are much more informative they are also more complex and it is more difficult to find evidence for them when the experimental effect is small. Since we don't know the data well enough and we don't know whether we will have the resolution for complex models we will use both simple common-effect models and random-effects model.

### Exclusion criteria 

- English fluency. 

1. Include everyone regardless of years of English experience (or other language in which the survey is administered) 
2. Exclude participants with less than 5 years of English experience (or other language in which the survey is administered) 

- Manipulation check.

1. Exclude no one based on the manipulation check. 
2. Exclude participants who did not correctly recall the target gender 

- Straigthlining.

1. Exclude no one based on pattern of responding
2. Exclude participants who always selected the same option on all items within each of the 5 scales


In total, there will be $2\times2\times2\times2= `r 2*2*2*2`$ conditions for the multiverse analysis.

Exclusion criteria:
b. always the same option on all items within each of the two longer scales (5+ items) ???

To assess whether we want to do an exclusion or no exclusion at all we suggest to only analyze the level if more than 5% of the sample are excluded. We assume that otherwise the operationalisation differences will not have a meaningful effect on the results. 

\readmoi{Do we also want to check if different exclusion criteria overlap?}

For the scales: items will be dropped when alpha < .40 until alpha > .40. 

## Moderator scales

1. News exposure scale (1-7 Likert scale)
- How frequently do you read news articles?
- To what extent are you familiar with the #MeToo movement?
- How often have you come across news articles about gender discrimination in the workplace? 
- How much exposure have you had to online commentary (e.g., Twitter, Facebook, etc) alleging biases against women in professional settings? 
- How much exposure have you had to mainstream news coverage (e.g., newspapers, television news programs) alleging biases against women in professional settings? 
- To what extent have you been actively following the #MeToo movement? 

2. Internal motivation to respond without sexism (1-7 Likert scale)
- I am personally motivated by my beliefs to be nonsexist toward women. 
- Being nonsexist toward women is important to my self-concept. 
- Because of my personal values, I believe that using stereotypes about women is wrong. 

3. External motivation to respond without sexism (1-7 Likert scale)
- Because of today’s PC (politically correct) standards I try to appear nonsexist toward women.
- I try to hide any negative thoughts about women in order to avoid negative reactions from others. 
- I attempt to appear nonsexist toward women in order to avoid disapproval from others.  

4. Beliefs about gender in the workplace (1-7 Likert scale)
- Women are more likely to be passed over for assignments in the workplace than men are
- Women experience more instances of bias in the workplace than men do
- Men tend to get more opportunities than women do in the workplace
- Do you believe there is more bias against women or against men in professional settings, limiting their chances for advancement? 
- Female managers face systematic gender discrimination in today’s workplaces. 

5. Sexist beliefs (1-7 Likert scale)
- It’s a fact that men are better suited for some	jobs than are women.
- Sometimes it’s the objective thing to do to hire a man rather than a woman.
- It’s a fact that men are better suited than women for the type of work the candidate 


# Model Specification and Predictions 

## Prior settings 

We think small effects in the predicted direction may still be meaningful. We therefore propose to use a scale of 0.25 for the effect of interest. A scale of 0.25 assumes an size effect that is 25% of the sampling noise (standard deviation), which is generally considered a small effect. For the variation between countries/labs we use a setting of 60% of the overall size of the effect, which means a scale of 0.15. 

## General Model Structure 

We will use Bayesian hierarchical modeling with participants nested in countries/labs. We will first construct an unconstrained model that includes all main parameters from the separate theories, which are free to vary in size and direction. In the primary analysis, we will used different ordinal constraints to capture the different theoretical predictions (see below). Bayes factor model comparison will be used to compare the models and determine what theory best predicts the empirical data. This method is based on the work by @haaf2018capturing. 

The base model for the gender and emotion effect on status conferral is: 
\[Y_{ijk} \sim N(\alpha_i + p_j \beta_i + r_j \gamma_i + w_j \zeta_i + l_j \omega_i + x_k \eta_i + u_{ik} \theta_{i1} + v_{ik} \theta_{2} + l_{jk} \theta_{i3} + m_{jk} \theta_{i4} + c_{jk} \theta_{i5} + d_{jk} \theta_{i6} + t_{ik} \theta_{i7}, \sigma^2),\]
where, 

- $\alpha_i$ is the baseline rating for $i$th lab
- $\beta_i$ is the target gender effect for $i$th lab
- $\gamma_i$ is the target emotion effect for $i$th lab
- $\zeta_i$ is the culture (East vs. West) effect for $i$th lab


- $\eta_i$ is the general experimental effect for $i$th region
- $\theta_{i1}$ is the $i$th region's experimental effect for US participants
- $\theta_{2}$ is the experimental effect for New England participants 
- $\theta_{i3}$ is the $i$th region's experimental effect for Protestant participants
- $\theta_{i4}$ is the $i$th region's experimental effect for highly religious participants
- $\theta_{i5}$ is the $i$th region's experimental effect for participants who endorse PWE
- $\theta_{i6}$ is the $i$th region's experimental effect for high SES participants
- $\theta_{i7}$ is the $i$th region's experimental effect for participants from self-expression cultures

c_j is the 

### Theoretical Predictions:

1. Null Model: angry men, sad men, angry women and sad women are all accorded equal status. 

\[Y_{ijk} \sim N(\alpha_i, \sigma^2),\]

2. Gender Stereotyping: while angry men are accorded higher status than sad men, angry women are accorded lower status than sad women. 
(main effect of gender, emotion effect for men, emotion effect for women?)

Common: 
\[Y_{ijk} \sim N(\alpha_i + x_j \beta_i + r_j \gamma_i +  w_j \zeta_i + l_j \omega_i + u_{ik} \theta_{1}, \sigma^2),\]
with $\theta_1 > 0$

Random: 
\[Y_{ijk} \sim N(\alpha_i + p_j \beta_i + r_j \gamma_i +  w_j \zeta_i + l_j \omega_i + u_{ik} \theta_{i1}, \sigma^2),\]
with all $\theta_{i1} > 0$

## Questions:

1. what do we expect the moderators to affect exactly? Main effects, interactions? 
2. just to be sure, we removed the order constraints for a main effect of gender, but this is given as key theoretical predictions of the Gender Stereotyping model in Table 1 (indicated by an asterisk). 

# References
